### 2014-10-10 fundamentals/intro.tex
dynamically loadable libraries implementation section closely follows katy's dissertation discussion on this topic. Some slight paraphrasing was employed to avoid self-plaigarism
editing intro

In order to characterize performance metrics, nuclear fuel cycle analysis 
requires calculation and optimization of myriad physical, nuclear, chemical, 
industrial, and political phenomena. Furthermore, complex systems such as 
nuclear process physics, facility deployment, and material routing each 
must be modeled simultaneously for even the simplest of nuclear fuel cycle 
simulations.

@@

>>>>

In order to characterize the performance of nuclear fuel cycle tecnhologies and performance metrics, nuclear fuel cycle analysis 
requires calculation and optimization of myriad physical, nuclear, chemical, 
industrial, and political phenomena. Furthermore, complex systems such as 
nuclear process physics, facility deployment, and material routing each 
must be modeled simultaneously for even the simplest of nuclear fuel cycle 
simulations.

@@

Associated with \Cyclus is Cycamore (the additional modules repository).
